---
title: "p8105_hw5_vd2392.Rmd"
output: github_document
---

## Setup 

##### General
```{r general_setup}
knitr::opts_chunk$set(
  echo = TRUE,
  include = TRUE,
  message = FALSE,
  warning = FALSE
)
```

##### Visualizations
```{r visualiztion_setup}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

##### Installations
```{r installations}
library(tidyverse)
library(ggridges)
library(patchwork)
library(readxl)
```

## Problem 1

Dataset: This dataset contains 52,000 criminal homicides over the past decade in 50 of the largest American cities. Among the variables of interest include location of the killing, whether an arrest was made and, in most cases, basic demographic information of each victim.

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )


```

#### Table Preview
```{r}
knitr::kable(head(aggregate_df), "simple", caption = "Source:")
```

Can I do a prop test for a single city?

```{r}
prop_test = prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

#### Table Preview
```{r}
knitr::kable(prop_test, "simple", caption = "Source:")
```

Try to iterate ........

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```


#### Table Preview
```{r}
knitr::kable(results_df, "simple", caption = "Source:")
```


```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

## Problem 2



```{r}

data_path = "data/p2_data/"

df = 
  tibble(
    file = list.files(data_path),
  )

knitr::kable(df, "simple", caption = "Source:")

```


#### Table Preview
```{r}


extract = function(path) {
 data = read_csv(path) %>% 
  janitor::clean_names()
 data
}


new = df %>% 
  mutate(
    path = str_c(data_path, file),
    data = as.vector(map_dfr(path, extract))
  )

new$data



```

### Part 3

```{r}

final = new %>% {
  bind_cols(select(., file:path), bind_rows(!!!.$data))
}

final = final  %>% 
  mutate(
    subject_id = case_when(
      substr(file, 0, 3) == "con" ~ paste("Control", substr(file, 5, 6), sep = "_"),
      substr(file, 0, 3) == "exp" ~ paste("Experimental", substr(file, 5, 6), sep = "_")
    ),
    treatment_arm = case_when(
      substr(file, 0, 3) == "con" ~ "Control",
      substr(file, 0, 3) == "exp" ~ "Experimental"
    )
  ) %>% 
  select(
    treatment_arm, subject_id, week_1:week_8
  ) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "result",
    names_prefix = "week_"
  ) %>% 
  mutate(
    week = as.numeric(week)
  )

final
#, color = subject_id
ggplot(data = final, aes(x = week, y = result, color = treatment_arm)) + 
  geom_point(data = final) + 
  geom_line(data = final, aes(x = week, y = result, color = treatment_arm))
```

```{r}





```

